A Bayesian statistical model is able to predict target-by-target selection behaviour in a human foraging task

### 2022-10-26 manuscriptRevisions2.tex
stupid changes

with $f(\phi_1, \phi_2) = \text{min}((\phi_1 - \phi_2) \% 2\pi, (\phi_2 - \phi_1) \% 2\pi)$. This model is implemented in a multi-level framework, allowing each of the four parameters to vary from participant to participant. Further details including priors and full code can be found with \cite{clarke2022foraging}.

>>>>

with $f(\phi_1, \phi_2) = \text{min}((\phi_1 - \phi_2) \% 2\pi, (\phi_2 - \phi_1) \% 2\pi)$ calculating the angular difference. $\text{atan2}$ is the direction of travel\footnote{For some reason, the editor insisted that re define atan2. This seems odd, as this is a simple funciton that children learn at school. But, it is a strange and varied world out there, so who knows.} This model is implemented in a multi-level framework, allowing each of the four parameters to vary from participant to participant. Further details including priors and full code can be found with \cite{clarke2022foraging}.
